Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-18 report/report.tex
Update todo
Add references to Nakata-Osaki and Joon

% Monday
% TODO: Edge distance algorithm, algorithm
% Collision study implementation
    % TODO: Figure detailing the steps in the point-matching algorithm

@@

Such procedural techniques have long been available.
\textbf{(Mũller et al, 2006)} present how to accomplish this using Shape Grammar: a method for automatically and iteratively constructing 3D models based in a hierarchical set of rules.
By starting with a crude volumetric model of a building and iteratively remodeling it from a set of shape grammars, a procedural model can structure the façade, add texture and add details for windows, doors and ornaments, and so on.
Shape grammars often work from a databank of 3D models and a set of hierarchical rules for how these can be pieced together.
This creates a possible generative space of many different models that can be created from the same data and rule set, and with the induction of random fluctuations, many different models can be generated from the same dataset and rules.
For simple presentation in e.g. animation and videogames or even urban planning software, such procedurally generated cities could very well be enough.
As said however, the big problem is that these features will rarely match real life, such models will be sufficient as long as one can be satisified with looking at rough representations of buildings and does not require additional knowledge about minor features.
Many studies urban development have been done before that requred detailed knowledge about a city's geometry, e.g. for the purposes of modeling heat development (***find reference) and reducing noise (**find reference).

It even turns out, by looking at such studies, that a lot of research in urban development require detailed morpological information that goes beyond simply knowing the geometry of the city.
Urban architects often work with morpological structures where a single feature, such as a city neighbourhood, can be examined from many different levels of perspective.
A neighbourhood can be analysed from the level of its city blocks, individual lots, properties or building limits, building facades or even indoor spaces.
Simlarily a road network can be analysed by looking at it either at its connectivity by viewing it a a simple 2D graph
But it might as well be seen as a hierarchical structure where primary roads branch off into sub-streets. 
The very unfortunate fact is that much of that morpological information is not present in the OSM dataset.
Furthermore, take the fact that even a single road can be comprised of many different sections with different purposes.
A single inner-city street for example, often contains sidewalks and lanes reserved for taxis or public transit, all of a certain placement and dimension that determines what type of traffic it can serve.
This type of representation is known as a multimodal structures, due to the possibility of incorporating mulitple modes of transportation, but it may even describe subtilities like building facades and distances between curbline and building lot.
OSM, while being an excellent source of city geometry, is simply not a sophisticated enough dataset to cater to all these possible areas of research.
\textbf{Stojanovski, 2019}
For media applications, such morppological and multimodal information could in theory be generated procedurally, by using shape grammars and some sort of wayfinding to create logical routes for different types of traffic.
But for urban planners requiring an exact morphological representation of some specification, this complementary data will have to be obtained from another dataset.

@@

@@

>>>>

% Monday
% Collision study implementation
    % TODO: Figure detailing the steps in the point-matching algorithm

@@

Such procedural techniques have long been available.
\textbf{(Mũller et al, 2006)} present how to accomplish this using Shape Grammar: a method for automatically and iteratively constructing 3D models based in a hierarchical set of rules.
By starting with a crude volumetric model of a building and iteratively remodeling it from a set of shape grammars, a procedural model can structure the façade, add texture and add details for windows, doors and ornaments, and so on.
Shape grammars often work from a databank of 3D models and a set of hierarchical rules for how these can be pieced together.
This creates a possible generative space of many different models that can be created from the same data and rule set, and with the induction of random fluctuations, many different models can be generated from the same dataset and rules.
For simple presentation in e.g. animation and videogames or even urban planning software, such procedurally generated cities could very well be enough.
As said however, the big problem is that these features will rarely match real life, such models will be sufficient as long as one can be satisified with looking at rough representations of buildings and does not require additional knowledge about minor features.
Many studies urban development have been done before that requred detailed knowledge about a city's geometry, e.g. for the purposes of modeling heat development
\textbf{(Nakata-Osaki, Souza and Rodrigues, 2018)}
and reducing noise.
\textbf{(Joon, Seo and Byung, 2011)}

It even turns out, by looking at such studies, that a lot of research in urban development require detailed morpological information that goes beyond simply knowing the geometry of the city.
Urban architects often work with morpological structures where a single feature, such as a city neighbourhood, can be examined from many different levels of perspective.
A neighbourhood can be analysed from the level of its city blocks, individual lots, properties or building limits, building facades or even indoor spaces.
Simlarily a road network can be analysed by looking at it either at its connectivity by viewing it a a simple 2D graph
But it might as well be seen as a hierarchical structure where primary roads branch off into sub-streets. 
The very unfortunate fact is that much of that morpological information is not present in the OSM dataset.
Furthermore, take the fact that even a single road can be comprised of many different sections with different purposes.
A single inner-city street for example, often contains sidewalks and lanes reserved for taxis or public transit, all of a certain placement and dimension that determines what type of traffic it can serve.
This type of representation is known as a multimodal structures, due to the possibility of incorporating mulitple modes of transportation, but it may even describe subtilities like building facades and distances between curbline and building lot.
OSM, while being an excellent source of city geometry, is simply not a sophisticated enough dataset to cater to all these possible areas of research.
\textbf{(Stojanovski, 2019)}
For media applications, such morppological and multimodal information could in theory be generated procedurally, by using shape grammars and some sort of wayfinding to create logical routes for different types of traffic.
But for urban planners requiring an exact morphological representation of some specification, this complementary data will have to be obtained from another dataset.

@@

\bibitem{joon-11}
Joon, H. K., Seo, I. C. and Byung, C. L. (2011) Noise impact assessment by utilizing noise map and GIS: A case study in the city of Chungju, Republic of Korea. Applied Acoustics, Volume 72, Issue 8. 544-550. ISSN 0003-682X.

@@

\bibitem{nakata-osaki-18}
Nakata-Osaki, C. M., Souza, L. C. L. and Rodrigues, D. S. (2018). THIS – Tool for Heat Island Simulation: A GIS extension model to calculate urban heat island intensity based on urban geometry. Computers, Environment and Urban Systems, Volume 67. 157-168. ISSN 0198-9715.
